\begin{thebibliography}{}
    \bibitem{metasploit}{
        \textbf{Author(s):} Metasploit.
        \textbf{Title:} \textit{Metasploit Docs}.
        \textbf{Retrieved from:} {\textit{\url{https://www.metasploit.com/}}}.
    }

    \bibitem{flask}{
        \textbf{Author(s):} Flask.
        \textbf{Title:} \textit{Metasploit Documentation}.
        \textbf{Retrieved from:} {\textit{\url{https://flask.palletsprojects.com/en/3.0.x/}}}.
    }

    \bibitem{pynput}{
        \textbf{Author(s):} Moses Palmér.
        \textbf{Title:} \textit{Pynput Documentation}.
        \textbf{Retrieved from:} {\textit{\url{https://pynput.readthedocs.io/en/latest/}}}.
    }

    \bibitem{emwh}{
        \textbf{Author(s):} Parkouss.
        \textbf{Title:} \textit{EMWH Documentation}.
        \textbf{Retrieved from:} {\textit{\url{https://github.com/parkouss/pyewmh}}}.
    }

    \bibitem{pycryptodome}{
        \textbf{Author(s):} Legrandin.
        \textbf{Title:} \textit{PyCryptodome Documentation}.
        \textbf{Retrieved from:} {\textit{\url{https://github.com/Legrandin/pycryptodome/}}}.
    }

    \bibitem{kernel_exploit}{
        \textbf{Author(s):} LiveOverflow.
        \textbf{Title:} \textit{Kernel Root Exploit via a ptrace() and execve() Race Condition}.
        \textbf{Retrieved from:} {\textit{\url{https://www.youtube.com/watch?v=qUh507Na9nk}}}.
    }

    \bibitem{race_condition}{
        \textbf{Author(s):} Red Hat, Inc.
        \textbf{Title:} \textit{Race Condition (CVE-2023-32257)}.
        \textbf{Retrieved from:} {\textit{\url{https://nvd.nist.gov/vuln/detail/CVE-2023-32257}}}.
    }

    \bibitem{string_exploit}{
        \textbf{Author(s):} LiveOverflow.
        \textbf{Title:} \textit{A simple Format String exploit example - bin 0x11}.
        \textbf{Retrieved from:} {\textit{\url{A simple Format String exploit example - bin 0x11}}}.
    }

    \bibitem{string_format}{
        \textbf{Author(s):} OWASP.
        \textbf{Title:} \textit{Format String Attack}.
        \textbf{Retrieved from:} {\textit{\url{https://owasp.org/www-community/attacks/Format_string_attack}}}.
    }

    \bibitem{preload_shared_library}{
        \textbf{Author(s):} Gustavo Lagos.
        \textbf{Title:} \textit{Is it possible to programatically preload a shared library?}.
        \textbf{Retrieved from:} {\textit{\url{https://stackoverflow.com/questions/68400690/is-it-possible-to-programatically-preload-a-shared-library}}}.
    }

    \bibitem{reverse_shell}{
        \textbf{Author(s):} TOKYONEON.
        \textbf{Title:} \textit{Pop a Reverse Shell with a Video File by Exploiting Popular Linux File Managers}.
        \textbf{Retrieved from:} {\textit{\url{https://null-byte.wonderhowto.com/how-to/pop-reverse-shell-with-video-file-by-exploiting-popular-linux-file-/managers-0196078/}}}.
    }

    \bibitem{worst_ransomware}{
        \textbf{Author(s):} ENOENT.
        \textbf{Title:} \textit{Analysing the worst ransomware - part 1}.
        \textbf{Retrieved from:} {\textit{\url{https://bitsdeep.com/posts/analysing-worst-ransomware-part-1/}}}.
    }

    \bibitem{upload_file}{
        \textbf{Author(s):} \textit{Unknown}.
        \textbf{Title:} \textit{Python Upload File}.
        \textbf{Retrieved from:} {\textit{\url{https://gtfobins.github.io/gtfobins/python/\#file-upload}}}.
    }

    \bibitem{basic_priv_esc}{
        \textbf{Author(s):} g0tmi1k.
        \textbf{Title:} \textit{Basic Privilege Escalation}.
        \textbf{Retrieved from:} {\textit{\url{https://blog.g0tmi1k.com/2011/08/basic-linux-privilege-escalation/}}}.
    }
\end{thebibliography}